FictionEro - Affective Impact of Fiction

### 2025-11-13 analysis/analysis.qmd
updated analysis
rest of analysis done with draft model

```{r}
# draft_model <- brms::brm(
#   formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
#   data = df2,
#   family = brms::zero_one_inflated_beta())

# g1 <- modelbased::estimate_grouplevel(arousal2)

@@

```{r}
g1 <- readRDS("draft_model_estimates.rds")

@@

```{r}
colors <- c("Intercept" = "#9C27B0")

p2_dvour <- g1 |> 
   mutate(Group = fct_relevel(Group, "Participant", "Item")) |>
  ggplot(aes(x = Median , y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Parameter, scales = "free", switch="both") +
  ggside::ggside(scales  = "free") +
  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```

@@

>>>>

```{r}
draft_model <- brms::brm(
  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
  data = df2,
  algorithm = "meanfield",
  family = brms::zero_one_inflated_beta())

g1 <- modelbased::estimate_grouplevel(draft_model)

@@

```{r}
# g1 <- readRDS("draft_model_estimates.rds")

@@

##### Study 1

```{r}
colors <- c("Intercept" = "#9C27B0", "ConditionAIMGenerated" = "#FF9800")

p2_dvour <- g1 |> 
   mutate(Group = fct_relevel(Group, "Participant", "Item"),
          Parameter = fct_relevel(Parameter, "Intercept", "ConditionAIMGenerated")) |>
  ggplot(aes(x = Median , y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Parameter, scales = "free", switch="both") +
  ggside::ggside(scales  = "free") +
  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```

##### Study 2

```{r}
colors <- c("Intercept" = "#9C27B0", "ConditionAIMGenerated" = "#FF9800")

p2_dvour <- g1 |> 
   mutate(Group = fct_relevel(Group, "Participant", "Item"),
          Parameter = fct_relevel(Parameter, "Intercept", "ConditionAIMGenerated")) |>
  ggplot(aes(x = Median , y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Parameter, scales = "free", switch="both") +
  ggside::ggside(scales  = "free") +
  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```

@@

- between random-slopes (effect of condition) and dispositional traits 
<!-- - look at mint and fiction choco analysis for correlation matrix -->

#### Study 1

```{r}

df_phase <- as.data.frame(g1) |>
  filter(Group == "Participant") |>
  mutate(Parameter = as.factor(Parameter)) |>
   pivot_wider(id_cols = Level, names_from = Parameter, values_from = c(Median, MAD, CI_low, CI_high),names_glue = "{Parameter}_{.value}"
  ) |>
  rename(Participant= Level)

head(g2_phase)

df_dispositional <- dfsub1 |>
  select(Participant, 
           BAIT_Videos, BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn) |>
  rename(Porn_factor = Porn)

head(g3_dispositional)

```{r}
make_cor <- function(df_phase, df_dispositional = NULL, 
                     qname_x = TRUE, qname_y = TRUE, 
                     textsize = 3, xcol = "#424242", ycol = "#424242") {

  # Identify common participants (if df_dispositional provided)
  if (!is.null(df_dispositional)) {
    common_ids <- intersect(df_phase$Participant, df_dispositional$Participant)
    df_phase <- df_phase |> filter(Participant %in% common_ids) |> arrange(Participant)
    df_dispositional <- df_dispositional |> filter(Participant %in% common_ids) |> arrange(Participant)
  }

  # Compute correlations
  # r <- df_phase |>
  #   select(ConditionAIMGenerated_Median, Intercept_Median) |>
  #   correlation::correlation(
  #     data2 = if (!is.null(df_dispositional)) df_dispositional |> select(-Participant) else NULL,
  #     p_adjust = "none",
  #     redundant = ifelse(is.null(df_dispositional), TRUE, FALSE)
  #   ) |>
  #   correlation::cor_sort() |>
  #   mutate(
  #     label = ifelse(p < .05, paste0(insight::format_value(r, lead_zero = FALSE, zap_small = TRUE)), ""),
  #     Parameter1 = as.factor(Parameter1),
  #     Parameter2 = as.factor(Parameter2)
  #   )

  r <- df_phase |>
  select(ConditionAIMGenerated_Median, Intercept_Median) |>
  correlation::correlation(
    data2 = if (!is.null(df_dispositional)) df_dispositional |> select(-Participant) else NULL,
    p_adjust = "none",
    redundant = ifelse(is.null(df_dispositional), TRUE, FALSE)
  ) |>
  correlation::cor_sort() |>
  mutate(
    # always show r, add '*' if p < .05
    label = paste0(
      insight::format_value(r, lead_zero = FALSE, zap_small = TRUE),
      ifelse(p < .05, "*", "")
    ),
    Parameter1 = as.factor(Parameter1),
    Parameter2 = as.factor(Parameter2)
  )

  # Clear diagonal labels
  r[as.character(r$Parameter1) == as.character(r$Parameter2), "label"] <- ""

  # Axis names
  xnames <- levels(r$Parameter1)
  ynames <- levels(r$Parameter2)

  # xcol <- case_when(
  #   str_detect(xnames, "Condition") ~ "#1565C0",
  #   str_detect(xnames, "Intercept") ~ "#6A1B9A",
  #   .default = xcol
  # )
  # ycol <- case_when(
  #   str_detect(ynames, "BAIT") ~ "#00838F",
  #   str_detect(ynames, "GAAIS") ~ "#C62828",
  #   str_detect(ynames, "AI_Knowledge") ~ "#EF6C00",
  #   .default = ycol
  # )

  # Bold emphasis (optional, minimal)
  xbold <- case_when(
    str_detect(xnames, "Condition") ~ "bold",
    str_detect(xnames, "Intercept") ~ "bold",
    .default = "plain"
  )
  ybold <- case_when(
    str_detect(ynames, "BAIT") ~ "bold",
    str_detect(ynames, "GAAIS") ~ "bold",
    str_detect(ynames, "Porn") ~ "bold",
    str_detect(ynames, "AI") ~ "bold",
    .default = "plain"
  )

  # Plot
  r |>
    ggplot(aes(x = Parameter1, y = Parameter2, fill = r)) +
    geom_tile() +
    geom_text(aes(label = label), size = textsize, lineheight = 0.9) +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(color = xcol, face = xbold),
      axis.text.y = element_text(color = ycol, face = ybold),
      legend.position = "none",
      axis.title = element_blank()
    )
}

p_corAI <- make_cor(df_phase, df_dispositional, qname_x = FALSE, qname_y = FALSE, textsize = 3)  +
  labs(title="Correlations between the effect of condition and dispositional traits") +
  theme(axis.title = element_blank())

p_corAI 
```

#### Study 2
